%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ONE FILE SAMPLE RESUME (SELF-CONTAINED)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[10pt,letterpaper]{article}

%------------------------------------------------
% PACKAGES
%------------------------------------------------
\usepackage{cmap}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\DisableLigatures{encoding = *, family = *}
\usepackage[none]{hyphenat}
\usepackage[parfill]{parskip}
\usepackage{array}
\usepackage{enumitem}
\usepackage{ifthen}
\usepackage{hyperref}
\usepackage[document]{ragged2e}
\usepackage[left=0.55in,top=0.6in,right=0.55in,bottom=0.55in]{geometry}

\urlstyle{same}
\linespread{1.02}
\renewcommand{\familydefault}{\rmdefault}

\hypersetup{
colorlinks=true,
linkcolor=blue,
urlcolor=blue
}

\pagestyle{empty}

%------------------------------------------------
% NAME + ADDRESS SYSTEM
%------------------------------------------------
\newcommand{\name}[1]{\def\myname{#1}}
\newcommand{\address}[1]{\def\myaddress{#1}}

\newcommand{\printname}{
\begin{center}
{\Large\bfseries\MakeUppercase{\myname}}
\end{center}
}

\newcommand{\printaddress}{
\begin{center}
\normalsize\myaddress
\end{center}
\vspace{0.2em}
}

%------------------------------------------------
% SECTION FORMAT
%------------------------------------------------
\newenvironment{rSection}[1]{
\vspace{0.4em}
{\sffamily\bfseries\Large #1}
\smallskip
\hrule
\vspace{0.3em}
\begin{list}{}{\setlength{\leftmargin}{0em}}
\item[]
}{
\end{list}
}

%------------------------------------------------
% SUBSECTION FORMAT
%------------------------------------------------
\newenvironment{rSubsection}[4]{
{\bf #1} \hfill {#2}
\ifthenelse{\equal{#3}{}}{}{
\\
{\em #3} \hfill {\em #4}
}
\smallskip
\begin{itemize}[leftmargin=1em, topsep=0.1em, itemsep=0.15em]
}{
\end{itemize}
\vspace{0.2em}
}

\setlist[itemize]{topsep=0.1em,itemsep=0.15em,leftmargin=1em}

%------------------------------------------------
% PERSONAL INFO (SAMPLE)
%------------------------------------------------
\name{First Name Last Name}

\address{
City, State |
(000) 000-0000 |
\href{mailto:email@example.com}{email@example.com} |
\href{https://linkedin.com/in/username}{linkedin.com/in/username} |
\href{https://github.com/username}{github.com/username}
}

%------------------------------------------------
% DOCUMENT START
%------------------------------------------------
\begin{document}

\RaggedRight
\printname
\printaddress

%------------------------------------------------
% SUMMARY
%------------------------------------------------
\begin{rSection}{Summary}
Software Engineer with experience building backend and frontend systems using modern web technologies. Skilled in API design, distributed systems, and cloud deployment. Focused on performance, scalability, and maintainable architecture across production environments.
\end{rSection}

\vspace{10pt}

%------------------------------------------------
% SKILLS
%------------------------------------------------
\begin{rSection}{Skills}
\begin{itemize}
\item \textbf{Programming}: Python, TypeScript, JavaScript, SQL, Java
\item \textbf{Backend}: Django, FastAPI, Flask, NodeJS, REST APIs
\item \textbf{Frontend}: React, NextJS, Vue, Tailwind CSS
\item \textbf{Databases}: PostgreSQL, MySQL, MongoDB, Redis
\item \textbf{Cloud}: AWS, Docker, Kubernetes, CI/CD
\item \textbf{Tools}: Git, Linux, Testing frameworks
\end{itemize}
\end{rSection}

\vspace{10pt}

%------------------------------------------------
% EXPERIENCE
%------------------------------------------------
\begin{rSection}{Experience}

\begin{rSubsection}{Software Engineer}{Jan 2023 -- Present}{Example Company}{Country}
\item Developed scalable backend services using Python and REST APIs.
\item Improved application performance through database optimization.
\item Implemented CI/CD pipelines for automated deployment.
\item Collaborated with frontend teams to deliver production features.
\end{rSubsection}

\begin{rSubsection}{Junior Developer}{Jan 2021 -- Dec 2022}{Sample Tech Inc}{Country}
\item Built web features using modern JavaScript frameworks.
\item Maintained internal tools and fixed production issues.
\item Wrote automated tests improving release stability.
\end{rSubsection}

\end{rSection}

\vspace{10pt}

%------------------------------------------------
% EDUCATION
%------------------------------------------------
\begin{rSection}{Education}

\textbf{Bachelor of Computer Science} \hfill 2017 -- 2021 \\
University Name, Country

\end{rSection}

\end{document}